method

### 2021-11-19 06_Paper/ER-ED/method.Rmd
added paragraph to statistics

All statistical analyses were perfomed using *RStudio* (version 1.4.1717) [@RStudioTeam2020]and *R* (version 4.1.0) [@RCore2020] for Windows.
The level of significance was set to $alpha$ = .05.
To examine impact of valence of emotional pictures on subjective arousal, an ANOVA with the factor valence (neutral and negative) for strategy active viewing was conducted.

>>>>

All statistical analyses were perfomed using *RStudio* (version 1.4.1717) [@RStudioTeam2020]and *R* (version 4.1.0) [@RCore2020] for Windows.
The level of significance was set to $alpha$ = .05.

*Effects of emotion regulation* <br>
To examine impact of valence of emotional pictures on subjective arousal, an ANOVA with the factor valence (neutral and negative) for strategy active viewing was conducted for behavioral data (subjective arousal ratings).
